Fig1

### 2020-04-17 analysis/figure-1.Rmd
better fig 1-4
now with fig and 2 togetehr

@@

# Figure 1. Experimental design, tSNE analysis, PCA, and prolactin

@@

@@

```{r fig1, fig.width=7, fig.height=6}

a <- plottsneelipse(chartsne, chartsne$tissue, allcolors) + labs(subtitle = "~ tissue")    
b <- plottsneelipse(chartsne, chartsne$sex, allcolors)   + labs(y = " ", subtitle = "~ tissue * sex")    
c <- plottsneelipse(ftsne, ftsne$tissue, allcolors ) + labs(y = " ", subtitle = "female ~ tissue")
d <- plottsneelipse(mtsne, mtsne$tissue, allcolors ) + labs(y = " ", subtitle = "male * tissue")

abcd <- plot_grid(a,b,c,d, nrow = 1, labels = c("b", "c", "d", "e"), label_size = 8 )

expdesign <- png::readPNG("../figures/images/fig1a_fig1a.png")
expdesign <- ggdraw() +  draw_image(expdesign, scale = 1)

abcde <- plot_grid(expdesign, abcd, nrow = 2, labels = c("a", "b"), label_size = 8, rel_heights = c(0.5,1))

h <- plottsneelipsev2(hyptsne, hyptsne$treatment, allcolors) + labs(subtitle = "hypothalamus ~ treatment")  + facet_wrap(~sex, scales = "free")
i <- plottsneelipsev2(pittsne, pittsne$treatment, allcolors ) + labs(subtitle = "pituitary ~ treatment", y = NULL) + facet_wrap(~sex, scales = "free") + theme(legend.position = )
j <- plottsneelipsev2(gontsne, gontsne$treatment, allcolors ) + labs(subtitle = "gonads ~ treatment", y = NULL)  + facet_wrap(~sex, scales = "free")

hij <- plot_grid(h,i,j, nrow = 1, labels = c("h", "i", "j"), label_size = 8)

fig1 <- plot_grid(abcde, hij, nrow = 2, rel_heights = c(0.6,0.4))
fig1

```{r}
write.csv(chartsne, "../../musicalgenes/data/tsne.csv")
```

>>>>

library(kableExtra) 
library(ggtext) # for italic fonts

@@

#  Experimental design, tSNE analysis, and bar chars

## tsne

@@

## DEGs

```{r allDEGs}
DEG_path <- "../results/DEseq2/"   # path to the data
DEG_files <- dir(DEG_path, pattern = "*DEGs") # get file names
DEG_pathfiles <- paste0(DEG_path, DEG_files)
#DEG_files

allDEG <- DEG_pathfiles %>%
  setNames(nm = .) %>% 
  map_df(~read_csv(.x), .id = "file_name") %>% 
  mutate(DEG = sapply(strsplit(as.character(file_name),'./results/DEseq2/'), "[", 2))  %>% 
  mutate(DEG = sapply(strsplit(as.character(DEG),'_diffexp.csv'), "[", 1))  %>% 
  mutate(tissue = sapply(strsplit(as.character(DEG),'\\.'), "[", 1)) %>%
  mutate(down = sapply(strsplit(as.character(DEG),'\\_'), "[", 3)) %>%
  mutate(up = sapply(strsplit(as.character(DEG),'\\_'), "[", 4)) %>%
  mutate(comparison = paste(down,up, sep = "_")) %>%
  mutate(sex = sapply(strsplit(as.character(sextissue),'\\_'), "[", 1)) %>%
  mutate(tissue = sapply(strsplit(as.character(sextissue),'\\_'), "[", 2)) %>%
dplyr::select(sex,tissue,comparison, direction, gene, lfc, padj, logpadj) 
head(allDEG)

allDEG$tissue <- factor(allDEG$tissue , levels = tissuelevel)
allDEG$comparison <- factor(allDEG$comparison , levels = comparisonlevels)
allDEG$direction <- factor(allDEG$direction, levels = charlevels)
```

@@

```{r fig1, fig.width=7.25, fig.height=7.25}

a <- png::readPNG("../figures/images/fig_fig1a.png")
a <- ggdraw() +  draw_image(a, scale = 1)

b <- plottsneelipse(chartsne, chartsne$sex, allcolors)   + labs(y = " ", subtitle = "~ tissue * sex")    
c <- plottsneelipse(ftsne, ftsne$tissue, allcolors ) + labs(y = " ", subtitle = "~ tissue, females only")
d <- plottsneelipse(mtsne, mtsne$tissue, allcolors ) + labs(y = " ", subtitle = "~ tissue, males only")

bcd <- plot_grid(b,c,d, nrow = 1, labels = c("B", "C", "D"), label_size = 8 )
abcd <- plot_grid(a, bcd, nrow = 2, labels = c("A"), label_size = 8, rel_heights = c(1,1))

e <- plottsneelipsev2(hyptsne, hyptsne$treatment, allcolors) + 
  labs( x = NULL)  + 
  facet_wrap(~sex, scales = "free")

g <- plottsneelipsev2(pittsne, pittsne$treatment, allcolors ) + 
  labs(  x = NULL) + 
  facet_wrap(~sex, scales = "free") +
  theme(strip.text = element_blank())

i <- plottsneelipsev2(gontsne, gontsne$treatment, allcolors ) + 
   facet_wrap(~sex, scales = "free") +
  theme(strip.text = element_blank()) +
  labs(x = "tSNE1 \n \n \n \n")

egi <- plot_grid(e,g,i, nrow = 3, rel_heights = c(1,1,1.4),
                 labels = c("E", "G", "I"), label_size = 8)

# hyp
f <- makebargraph("hypothalamus","DEGs", 0, 1250) + 
  theme(axis.text.x = element_blank(), 
        axis.title.x = element_blank())  
# pit
h <- makebargraph("pituitary","DEGs", 0, 1250)  +  
  theme(axis.text.x = element_blank(), 
        axis.title.x = element_blank(), 
        strip.text.x = element_blank())  
# gon
j <- makebargraph("gonad","DEGs", 0, 1250) +  
  theme(strip.text.x = element_blank()) +
  scale_x_discrete(labels = comparisonlabels)

fhj <- plot_grid(f,h,j, nrow = 3, rel_heights = c(1,1,1.4),
                 labels = c("F", "H", "J"), label_size = 8)

efghij <- plot_grid(egi, fhj, nrow = 1, align = "h", rel_widths = c(1.5,2))

fig1 <- plot_grid(abcd, efghij, nrow = 2, rel_heights = c(1,1.5))
fig1
```

```{r}
#write.csv(chartsne, "../../musicalgenes/data/tsne.csv")
```
